Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-16 analysis/paper/paper.Rmd
don't cache R output
This was causing the table of scoring criteria to not update

opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  dev = c("postscript"),
  fig.width = 3.31,
  fig.height = 3.31,
  out.width = "100%",
  dpi = 300,
  comment = "#>",
  dev = "cairo_pdf",
  cache = TRUE
)
```

>>>>

opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  dev = c("postscript"),
  fig.width = 3.31,
  fig.height = 3.31,
  out.width = "100%",
  dpi = 300,
  comment = "#>",
  dev = "cairo_pdf",
  cache = FALSE
)
```
